Abstract Data Type Inference

### 2015-03-22 inference.tex
Better titles.
Soft description of the formulas.
Formula example.

\section{Refinement \& ADT Inference}
\label{sec:inference}

@@

  \item a function symbol $\mathsf{m}$ for matching, and

  \item predicate symbols $\mathsf{c}$ and $\mathsf{<}$ for completion and
  order.

@@

  TODO HISTORY FORMULA EXAMPLE

>>>>

\section{The Symbolic ADT Inference Problem}
\label{sec:inference}

@@

  \item function symbols ${\sf f}$ and ${\sf m}$ for labels and matching, and

  \item predicate symbols ${\sf c}$, ${\sf um}$, and ${\sf <}$ for completion,
  non-matching, and order.

@@

  The following history formula is satisfied by histories in which no write
  operation happens between a pair of matching write and read operations:
  \begin{align*}
    \forall x, y, z.\ 
    & {\sf c}(x) \land {\sf f}(x) = \mathrm{write} \land {\sf m}(x) = x \\
    & \land {\sf c}(y) \land {\sf f}(y) = \mathrm{write} \land {\sf m}(y) = y \\
    & \land {\sf c}(z) \land {\sf f}(z) = \mathrm{read} \land {\sf m}(z) = x \\
    & \land x < y 
      \implies z < y
  \end{align*}
  This is one of several requirements of atomic single-value register ADTs,
  which is satisfied by certain linearizations of histories $H(e_2)$ and
  $H(e_3)$ of Example~\ref{ex:histories-of-executions}, yet not $H(e_1)$.
